Hypertension and microbiome

### 2019-09-30 articletwo.Rmd
Typo
Save dds

```{r deseq2}
pseq.genus.core.deseq <-  prune_taxa(taxa(pseq.genus.core), pseq.genus)

dds.data <- phyloseq_to_deseq2(pseq.genus.core.deseq,
                               as.formula(sprintf("~ %s + %s", "HT", paste0(var.CL, collapse = "+"))))

ds2 <- estimateSizeFactors(dds.data, type="poscounts")

dds <- DESeq(ds2, fitType='mean', parallel = TRUE, BPPARAM=MulticoreParam(16))

saveRDS(dds, file = "rds/dds.rds")
#dds <- readRDS(file = "rds/dds.rds")

>>>>

```{r deseq2}
if (!file.exists("rds/dds.rds")) {
    pseq.genus.core.deseq <-  prune_taxa(taxa(pseq.genus.core), pseq.genus)
    dds.data <- phyloseq_to_deseq2(pseq.genus.core.deseq,
                                   as.formula(sprintf("~ %s + %s", "HYPERTENSION", paste0(var.CL, collapse = "+"))))
    ds2 <- estimateSizeFactors(dds.data, type="poscounts")
    dds <- DESeq(ds2, fitType='mean', parallel = TRUE, BPPARAM=MulticoreParam(16))
    saveRDS(dds, file = "rds/dds.rds")
} else {
    dds <- readRDS(file = "rds/dds.rds")
}
